---
title: "Simulation Outputs"
output: html_notebook
---

!!!!!!!! REMOVE X AXIS !!!!!!!!!!

```{r}
### Libraries
library(dplyr); library(ggplot2); library(ggpubr)
#Total population
N <- 170 + 174
# ==============================================================================
# FUNCTIONS
# ==============================================================================
# Read Simulations
# ------------------------------------------------------------------------------
ReadSims <- function(dir){
  # dir = paste0(p, "00/EC/")
  f <- list.files(dir, full.names = TRUE)
  L <- lapply(1:length(f), function(x){
    read.csv(f[x], fileEncoding = 'UTF-8') %>% # read files
      mutate(Sim = x, day = ceiling(cycle/24)) %>% # create variable for sim number and day
      group_by(Sim, day) %>% # group by simulation and day
      summarise_all(.funs = max) %>%# get the max for all the records.
      ungroup()
    })
  
  N_sim <- lapply(L, nrow) %>% unlist() %>% max(.)
  
  L <- lapply(L, function(x){
    d <- N_sim - nrow(x)
      x %>%
        slice(c(1:nrow(.), rep(nrow(.), each = d))) %>%
        mutate(day = 1:n())
  })
  L %>%
    do.call(rbind, .)
}
# Functions for getting quantiles
# ------------------------------------------------------------------------------
Q05 <- function(sims) quantile(sims, 0.05)
Q25 <- function(sims) quantile(sims, 0.25)
Q75 <- function(sims) quantile(sims, 0.75)
Q95 <- function(sims) quantile(sims, 0.95)

# Function for summarizing the cycles
# ------------------------------------------------------------------------------
CycleSums <- function(sims){
  # sims = D00
  cycle_IQR <- sims %>%
    dplyr::select(-Sim) %>%
    group_by(day) %>%
    summarise_all(.funs = c(Median = median, Q25 = Q25, Q75 = Q75))
  
  cycle_TTE <- sims %>%
    group_by(Sim) %>%
    filter(I == max(I)) %>%
    filter(cycle == max(cycle)) %>%
    mutate(day = floor(cycle/24),
           Cumulative_I = Cumulative_I_r + Cumulative_I_s,
           InfectionRate = Cumulative_I/N)
  
  return(list(cycle_IQR = cycle_IQR, cycle_TTE = cycle_TTE))
}

# Function for the plots
# ------------------------------------------------------------------------------
PlotCycles <- function(sims, var, col, y_lim){
  # sims = D00; var = "I"; col = "red3"
  # y_lab = ifelse(grepl("_P", var), "Infected \n pig herds", "Infected \n wild boar")
  p = sims %>%
    CycleSums() %>%
    .$cycle_IQR %>%
    ggplot(aes(x = day)) +
    geom_line(aes(y = eval(parse(text = paste0(var, '_Median')))),
      col = col, lwd = 1) +
    geom_ribbon(aes(
      ymin = eval(parse(text = paste0(var, '_Q25'))),
      ymax = eval(parse(text = paste0(var, '_Q75')))),
      alpha = 0.3, fill = col) +
    ylab("Number of Infected") +
    theme_minimal() 
    # ylab(y_lab) +
  #   xlab("Days") +
  #   theme(legend.position = "none",
  #     axis.title.y = element_text(angle = 0, vjust = 0.5))
  # if( !missing(y_lim) ) p = p + ylim(y_lim)
  p
  
}
#### Function for time to eradication ####
#----------------------------------------#
TE_data <- function(data){
  data %>%
    mutate(day = floor(cycle/24)) %>%
    group_by(Sim, day) %>%
    summarise(I = max(I)) %>%
    group_by(Sim) %>%
    filter(I == max(I)) %>%
    filter(day == min(day))
}

#### Plot the outputs ####
#-------------------------------#
Plots <- function(x, main = ''){
  ##### NUMBER OF INFECTED ####
  CumI_p <- x %>%
  ggplot() +
  geom_boxplot(aes(y = InfectionRate, fill = Scenario)) +
  scale_fill_manual(values = ColPal) +
  ylab("Infection rate") +
  ggtitle("Epidemic Size")
  ##### EPIDEMIC LENGTH ####
  EpiL_p <- x %>% 
    ggplot() +
  geom_histogram(aes(day, fill = Scenario)) +
  scale_fill_manual(values = ColPal) +
  facet_grid(~Scenario) +
  ggtitle(" Epidemic duration")

  if(length(unique(x$Scenario)) == 1){
    ggarrange(CumI_p, EpiL_p, ncol = 2, common.legend = T) %>%
      annotate_figure(text_grob(main, color = "grey20", face = "bold", size = 14)) 
  }else{
    ggarrange(CumI_p, EpiL_p, nrow = 2, common.legend = T) %>%
      annotate_figure(text_grob(main, color = "grey20", face = "bold", size = 14)) 
  }
}

#### Summary table ####
#-------------------------------#
Sum_Tbl <- function(x){
  x %>%
    group_by(Scenario) %>%
    summarise_at(.vars = c('InfectionRate', 'day', 'Cumulative_I', 'Cumulative_I_r', 'Cumulative_I_s', 'Cumulative_H'), .funs = c(m = median, Q05 = Q05, Q95 = Q95)) %>%
    mutate(across(where(is.numeric), ~round(., 2)),
           InfectionRate = paste0(InfectionRate_m, ' (', InfectionRate_Q05, ',', InfectionRate_Q95, ')'),
           day = paste0(day_m, ' (', day_Q05, ',', day_Q95, ')'),
           Cumulative_I = paste0(Cumulative_I_m, ' (', Cumulative_I_Q05, ',', Cumulative_I_Q95, ')'),
           Cumulative_I_r = paste0(Cumulative_I_r_m, ' (', Cumulative_I_r_Q05, ',', Cumulative_I_r_Q95, ')'),
           Cumulative_I_s = paste0(Cumulative_I_s_m, ' (', Cumulative_I_s_Q05, ',', Cumulative_I_s_Q95, ')'),
           Cumulative_H = paste0(Cumulative_H_m, ' (', Cumulative_H_Q05, ',', Cumulative_H_Q95, ')'),) %>%
    select(Scenario, day, InfectionRate, Cumulative_I, Cumulative_I_r, Cumulative_I_s, Cumulative_H)
}
```

!!!!! Chek reparametrization of PPE use distribution (suggested: 0.9 staff, 0.75 residents) and infection rates (start from 0.5)
Make smaller epidemics with less PPE use (so the PPE effect impact becomes smaller)

```{r Test}
p <- "../../Data/SimsOut/Test/"
ColPal <- c("grey40")
### Test
Db <- ReadSims(p)
Sb <- PlotCycles(Db, var = "I", col = "red3")
Ib <- CycleSums(Db) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Baseline')

BTbl <- Sum_Tbl(Ib)
BTbl
Plots(Ib, 'Baseline Scenario')
```


# Baseline

| Name                     | Value              | Reference|
|--------------------------|--------------------|----------|
|Shedding probability      |    0.56            |          |
|Transmission probability  |    0.56            |          |
|Asymptomatic probability  |    0.25            |          |
|Introduction probability  |    0.1            |          |
|Test detection probability| $80\%$             | $^a$     |
| Frequency of testing     |   Weekly           | $^a$     |
| Proportion of Staff tested| $90\%$            | $^a$     |
| Proportion of Residents tested| $33.3%$       | $^a$     |
| PPE Effect ($OR_\pi$)    | 0.34089            |[@Chu2020]$^a$|
| Proportion of Resident PPE| $95\%$            | $^a$     |
| Proportion of Staff PPE  | $99\%$             | $^a$     |
| Vaccine effect ($OR_\upsilon$)| 0.0493        |[@Pfizer2020]$^a$|
| Vaccine effect ($OR_\upsilon$)| 0.0493        |[@Pfizer2020]$^a$|
| Proportion of Resident Vaccine| $0\%$            | $^a$     |
| Proportion of Staff Vaccine  | $0\%$             | $^a$     |
| Vaccine immunity duration| $120\ days$        | $^a$         |
|First dose effect        |     $60\%$          | $^a$         |


```{r}
p <- "../../Data/SimsOut/Baseline/"
ColPal <- c("grey40")
### 75% Detection Probability
Db <- ReadSims(p)
Sb <- PlotCycles(Db, var = "I", col = "red3")
Ib <- CycleSums(Db) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Baseline')

BTbl <- Sum_Tbl(Ib)
BTbl
Plots(Ib, 'Baseline Scenario') %>%
  ggsave(filename = "../../Documentation/Figures/SensitivityAnalysis/Baseline.png", width = 8, height = 4)
```



# Sensitivity analysis
## Transmission probability

00 - 0.54
01 - 0.58
02 - 0.64

```{r Transmission}
p <- "../../Data/SimsOut/SensitivityAnalysis/TransmissionProbability/"
ColPal <- c("#B284E3", "grey40", "#F28C8C")
### 3% Transmission Probability
D00 <- ReadSims(paste0(p, "Low/"))
S00 <- PlotCycles(D00, var = "I", col = "red3")
I00 <- CycleSums(D00) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Low transmission')
### 7% Introduction Probability
D01 <- ReadSims(paste0(p, "High/"))
S01 <- PlotCycles(D01, var = "I", col = "red3")
I01 <- CycleSums(D01) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'High transmission')
# ### 10% Introduction Probability
# D02 <- ReadSims(paste0(p, "02/"))
# S02 <- PlotCycles(D02, var = "I", col = "red3")
# I02 <- CycleSums(D02) %>%
#   .$cycle_TTE %>%
#   mutate(Scenario = 'High transmission')

x <- rbind(I00, Ib, I01) %>%
  mutate(Scenario = factor(Scenario, levels = c('Low transmission', 'Baseline', 'High transmission'))) 

TTbl <- Sum_Tbl(x)
TTbl
x %>%
  Plots('Transmission Probability') %>%
  ggsave(filename = "../../Documentation/Figures/SensitivityAnalysis/Transmission.png", width = 9, height = 5)
```


## Introduction probability

00 - 0.01
01 - 0.05
02 - 0.1

```{r Introduction}
p <- "../../Data/SimsOut/SensitivityAnalysis/IntroductionProbability/"
ColPal <- c("#704500", 'grey40', "#076600")
### 1% Introduction Probability
D00 <- ReadSims(paste0(p, "Low/"))
S00 <- PlotCycles(D00, var = "I", col = "red3")
I00 <- CycleSums(D00) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Low Introduction Probability')
### 10% Introduction Probability
D01 <- ReadSims(paste0(p, "High/"))
S01 <- PlotCycles(D01, var = "I", col = "red3")
I01 <- CycleSums(D01) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'High Introduction Probability')
### 10% Introduction Probability
# D02 <- ReadSims(paste0(p, "02/"))
# S02 <- PlotCycles(D02, var = "I", col = "red3")
# I02 <- CycleSums(D02) %>%
#   .$cycle_TTE %>%
#   mutate(Scenario = '10% Introduction Probability')

x <- rbind(I00, Ib, I01) %>%
  mutate(Scenario = factor(Scenario, levels = c('Low Introduction Probability', 'Baseline', 'High Introduction Probability'))) 

ITbl <- Sum_Tbl(x)
ITbl

x %>%
  Plots(main = "Probability of Introduction") %>%
  ggsave(filename = "../../Documentation/Figures/SensitivityAnalysis/Introduction.png", width = 9, height = 5)
```

## Detection probability

00 - 75% detection probability
01 - 85% detection probability
02 - 95% Detection probability

```{r DetectionProbability SA}
p <- "../../Data/SimsOut/SensitivityAnalysis/DetectionProbability/"
ColPal <- c("#00827E", 'grey40', "#00CFB7")
### 75% Detection Probability
D00 <- ReadSims(paste0(p, "Low/"))
S00 <- PlotCycles(D00, var = "I", col = "red3")
I00 <- CycleSums(D00) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Low Detection Probability')
### 85% Detection Probability
D01 <- ReadSims(paste0(p, "High/"))
S01 <- PlotCycles(D01, var = "I", col = "red3")
I01 <- CycleSums(D01) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'High Detection Probability')
### 95% Detection Probability
# D02 <- ReadSims(paste0(p, "02/"))
# S02 <- PlotCycles(D02, var = "I", col = "red3")
# I02 <- CycleSums(D02) %>%
#   .$cycle_TTE %>%
#   mutate(Scenario = '95% Detection Probability')

x <- rbind(I00, Ib, I01) %>%
  mutate(Scenario = factor(Scenario, levels = c('Low Detection Probability', 'Baseline', 'High Detection Probability')))

DTbl <- Sum_Tbl(x)
DTbl
x %>%
  Plots(main = "Probability of Detection") %>%
  ggsave(filename = "../../Documentation/Figures/SensitivityAnalysis/ProbDetection.png", width = 9, height = 5)
```

## Effect of Face masks (PPE)

00 - LB
01 - Estimate
02 - UB (0.2408)

```{r FaceMasks}
p <- "../../Data/SimsOut/SensitivityAnalysis/FaceMasks/"
ColPal <- c("#5C9669", "#6A918C", "#7280B3")
### 1% Introduction Probability
D00 <- ReadSims(paste0(p, "High/"))
S00 <- PlotCycles(D00, var = "I", col = "red3")
I00 <- CycleSums(D00) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'High effect PPE')
### 5% Introduction Probability
D01 <- ReadSims(paste0(p, "Low/"))
S01 <- PlotCycles(D01, var = "I", col = "red3")
I01 <- CycleSums(D01) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Low effect PPE')

x <- rbind(I00, Ib, I01) %>%
  mutate(Scenario = factor(Scenario, levels = c('High effect PPE', 'Baseline', 'Low effect PPE'))) 

PPETbl <- Sum_Tbl(x)
PPETbl
x %>% 
  Plots('Effect of PPE') %>%
  ggsave(filename = "../../Documentation/Figures/SensitivityAnalysis/PPE.png", width = 9, height = 5)
```


## Testing Frequency

```{r}
p <- "../../Data/SimsOut/SensitivityAnalysis/TestingFreq/"
ColPal <- c("#5C9669", "#6A918C", "#7280B3")
### 1% Introduction Probability
D00 <- ReadSims(paste0(p, "Testing5/"))
S00 <- PlotCycles(D00, var = "I", col = "red3")
I00 <- CycleSums(D00) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Every 5 days')
### 5% Introduction Probability
D01 <- ReadSims(paste0(p, "Testing3/"))
S01 <- PlotCycles(D01, var = "I", col = "red3")
I01 <- CycleSums(D01) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Every 3 days')

x <- rbind(I00, Ib, I01) %>%
  mutate(Scenario = factor(Scenario, levels = c('Baseline', 'Every 5 days', 'Every 3 days'))) 

TFTbl <- Sum_Tbl(x)
TFTbl
x %>% 
  Plots('Testing Frequency') %>%
  ggsave(filename = "../../Documentation/Figures/SensitivityAnalysis/TestingFreq.png", width = 9, height = 5)
```


## Vaccine Effect

```{r}
p <- "../../Data/SimsOut/SensitivityAnalysis/VaccineEffect/"

ColPal <- c("#5C9669", "#6A918C", "#7280B3")
### Same vaccine effect for residents and staff
D00 <- ReadSims(paste0(p, "Equal/"))
S00 <- PlotCycles(D00, var = "I", col = "red3")
I00 <- CycleSums(D00) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Same vaccine effect')
### Different vaccine effect for residents and staff (Pfizer)
D01 <- ReadSims(paste0(p, "Pfizer/"))
S01 <- PlotCycles(D01, var = "I", col = "red3")
I01 <- CycleSums(D01) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Pfizer')
### Different vaccine effect for residents and staff (Pfizer)
D02 <- ReadSims(paste0(p, "Moderna/"))
S02 <- PlotCycles(D02, var = "I", col = "red3")
I02 <- CycleSums(D02) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Moderna')

x <- rbind(I00, I01, I02) %>%
  mutate(Scenario = factor(Scenario, levels = c('Same vaccine effect', 'Pfizer', 'Moderna'))) 

VeTbl <- Sum_Tbl(x)
VeTbl
x %>%
  Plots('Vaccine Effect') %>%
  ggsave(filename = "../../Documentation/Figures/SensitivityAnalysis/VaccinationEf.png", width = 9, height = 5)
```


### Summary 

```{r SA Summary}
rbind(BTbl, TTbl, ITbl, DTbl, PPETbl, TFTbl, VeTbl) %>%
  distinct() %>%
write.csv(., "../../Documentation/Tables/SA_sum.csv", row.names = F)
```




# Scenario Modeling


```{r}
p <- "../../Data/SimsOut/Scenarios/"

ColPal <- c("#5C9669", "#6A918C", "#7280B3")
### Same vaccine effect for residents and staff
D00 <- ReadSims(paste0(p, "S01/"))
S00 <- PlotCycles(D00, var = "I", col = "red3")
I00 <- CycleSums(D00) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Resident priority')
### Different vaccine effect for residents and staff (Pfizer)
D01 <- ReadSims(paste0(p, "S02/"))
S01 <- PlotCycles(D01, var = "I", col = "red3")
I01 <- CycleSums(D01) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Staff priority')
### Different vaccine effect for residents and staff (Pfizer)
# D02 <- ReadSims(paste0(p, "Moderna/"))
# S02 <- PlotCycles(D02, var = "I", col = "red3")
# I02 <- CycleSums(D02) %>%
#   .$cycle_TTE %>%
#   mutate(Scenario = 'Moderna')

x <- rbind(I00, I01) %>%
  mutate(Scenario = factor(Scenario, levels = c('Resident priority', 'Staff priority'))) 

VdTbl <- Sum_Tbl(x)
VdTbl
x %>%
  Plots('Vaccine Distribution') %>%
  ggsave(filename = "../../Documentation/Figures/Scenarios/VaccineDist.png", width = 9, height = 5)
```



## Testing Frequency

```{r}
p <- "../../Data/SimsOut/Scenarios/TestingFreq/"
ColPal <- c("#5C9669", "#6A918C", "#7280B3")
### Same vaccine effect for residents and staff
D00 <- ReadSims(paste0(p, "00/"))
S00 <- PlotCycles(D00, var = "I", col = "red3")
I00 <- CycleSums(D00) %>%
  .$cycle_TTE %>%
  mutate(Scenario = '7 days')
### Different vaccine effect for residents and staff (Pfizer)
D01 <- ReadSims(paste0(p, "01/"))
S01 <- PlotCycles(D01, var = "I", col = "red3")
I01 <- CycleSums(D01) %>%
  .$cycle_TTE %>%
  mutate(Scenario = '5 days')
### Different vaccine effect for residents and staff (Pfizer)
D02 <- ReadSims(paste0(p, "02/"))
S02 <- PlotCycles(D02, var = "I", col = "red3")
I02 <- CycleSums(D02) %>%
  .$cycle_TTE %>%
  mutate(Scenario = '3 days')

rbind(I00, I01, I02) %>%
  mutate(Scenario = factor(Scenario, levels = c('7 days', '5 days', '3 days'))) %>%
  Plots('Testing Frequency') %>%
  ggsave(filename = "../../Documentation/Figures/Scenarios/TestingFreq.png", width = 9, height = 5)
```

## Vaccine distribution

### Low Community spread
```{r Low spread}
p <- "../../Data/SimsOut/Scenarios/VaccineDistrib/VaccineDistrib_01/"
ColPal <- c("#5C9669", "#6A918C", "#7280B3")
### Same vaccine effect for residents and staff
D00 <- ReadSims(paste0(p, "00/"))
S00 <- PlotCycles(D00, var = "I", col = "red3")
I00 <- CycleSums(D00) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'I00')
### Different vaccine effect for residents and staff (Pfizer)
D01 <- ReadSims(paste0(p, "01/"))
S01 <- PlotCycles(D01, var = "I", col = "red3")
I01 <- CycleSums(D01) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'I01')
### Different vaccine effect for residents and staff (Pfizer)
D02 <- ReadSims(paste0(p, "02/"))
S02 <- PlotCycles(D02, var = "I", col = "red3")
I02 <- CycleSums(D02) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'I02')

rbind(I00, I01, I02) %>%
  mutate(Scenario = factor(Scenario, levels = c('I00', 'I01', 'I02'))) %>%
  Plots("Vaccine Distribution Low Community Transmission")

# %>%
#   ggsave(filename = "../../Documentation/Figures/Scenarios/VD_Low.png", width = 9, height = 5)
```

### Med Community Spread

```{r Ve High spread}
p <- "../../Data/SimsOut/Scenarios/VaccineDistrib/VaccineDistrib_05/"
ColPal <- c("#5C9669", "#6A918C", "#7280B3")
### Same vaccine effect for residents and staff
D03 <- ReadSims(paste0(p, "00/"))
S03 <- PlotCycles(D03, var = "I", col = "red3")
I03 <- CycleSums(D03) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'I03')
### Different vaccine effect for residents and staff (Pfizer)
D04 <- ReadSims(paste0(p, "01/"))
S04 <- PlotCycles(D04, var = "I", col = "red3")
I04 <- CycleSums(D04) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'I04')
### Different vaccine effect for residents and staff (Pfizer)
D05 <- ReadSims(paste0(p, "02/"))
S05 <- PlotCycles(D05, var = "I", col = "red3")
I05 <- CycleSums(D05) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'I05')

rbind(I03, I04, I05) %>%
  mutate(Scenario = factor(Scenario, levels = c('I03', 'I04', 'I05'))) %>%
  Plots("Vaccine Distribution High Community Transmission")
# %>%
#   ggsave(filename = "../../Documentation/Figures/Scenarios/VD_High.png", width = 9, height = 5)
```
### High Community Spread

```{r Ve Higher spread}
p <- "../../Data/SimsOut/Scenarios/VaccineDistrib/VaccineDistrib_10/"
ColPal <- c("#5C9669", "#6A918C", "#7280B3")
### Same vaccine effect for residents and staff
D03 <- ReadSims(paste0(p, "00/"))
S03 <- PlotCycles(D03, var = "I", col = "red3")
I03 <- CycleSums(D03) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'I03')
### Different vaccine effect for residents and staff (Pfizer)
D04 <- ReadSims(paste0(p, "01/"))
S04 <- PlotCycles(D04, var = "I", col = "red3")
I04 <- CycleSums(D04) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'I04')
### Different vaccine effect for residents and staff (Pfizer)
D05 <- ReadSims(paste0(p, "02/"))
S05 <- PlotCycles(D05, var = "I", col = "red3")
I05 <- CycleSums(D05) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'I05')

rbind(I03, I04, I05) %>%
  mutate(Scenario = factor(Scenario, levels = c('I03', 'I04', 'I05'))) %>%
  Plots("Vaccine Distribution High Community Transmission")

# %>%
#   ggsave(filename = "../../Documentation/Figures/Scenarios/VD_High.png", width = 9, height = 5)
```

```{r}
Nsim <- 30
rbind(I00, I01, I02, I03, I04, I05) %>%
  mutate(Cumulative_I = Cumulative_I_r + Cumulative_I_s, 
         InfectionRate = Cumulative_I/N,
         HospRate = Cumulative_H/N) %>%
  group_by(Scenario) %>%
  summarise_at(.vars = c('InfectionRate', 'HospRate', 'day'), .funs = mean)
```




## Scenario 1

## Scenario 2






# |------ Legacy Code (prvious work) ------|

# |===TEST====|
```{r}
p <- "../../Data/SimsOut/Test/"
ColPal <- c("grey70")
### 75% Detection Probability
D00 <- ReadSims(p)
S00 <- PlotCycles(D00, var = "I", col = "red3")
I00 <- CycleSums(D00) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Test')
##### NUMBER OF INFECTED ####
CumI_p <- rbind(I00) %>%
  mutate(Cumulative_I = Cumulative_I_r + Cumulative_I_s) %>%
  ggplot() +
  geom_boxplot(aes(y = Cumulative_I/N, fill = Scenario)) +
  scale_fill_manual(values = ColPal) +
  ylab("Infection rate") +
  ggtitle("Epidemic Size")
##### EPIDEMIC LENGTH ####
EpiL_p <- rbind(I00) %>% 
  ggplot() +
  geom_histogram(aes(day, fill = Scenario)) +
  scale_fill_manual(values = ColPal) +
  facet_grid(~Scenario) +
  ggtitle(" Epidemic duration")

ggarrange(CumI_p, EpiL_p, ncol = 2, common.legend = T) %>%
  annotate_figure(text_grob("TEST Scenario", color = "grey20", face = "bold", size = 14)) 
```


## Use of PPE

### Effectiveness of PPE

```{r}
p <- "../../Data/SimsOut/PPE/"
ColPal <- c("#FF4040", "#FFA024", "#FFC64C", "#D6E020")
### USE OF PPE by 90% of population with a 60% of effectiveness
D00 <- ReadSims(paste0(p, "00/EC/"))
S00 <- PlotCycles(D00, var = "I", col = "red3")
I00 <- CycleSums(D00) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Low PPE Effect')
### USE OF PPE by 90% of population with a 60% of effectiveness
D01 <- ReadSims(paste0(p, "01/EC/"))
S01 <- PlotCycles(D01, var = "I", col = "red3")
I01 <- CycleSums(D01) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'High PPE Effect')
### USE OF PPE by 90% of population with a 80% of effectiveness
D02 <- ReadSims(paste0(p, "02/EC/"))
S02 <- PlotCycles(D02, var = "I", col = "red3")
I02 <- CycleSums(D02) %>%
  .$cycle_TTE %>%
  mutate(Scenario = '85% PPE Effect')

#### Infected curve ####
S00;S01;S02
##### NUMBER OF INFECTED ####
rbind(I00, I01, I02) %>%
  ggplot() +
  geom_boxplot(aes(y = Cumulative_I_r, fill = Scenario)) +
  scale_fill_manual(values = ColPal) +
  ggtitle("Epidemic Size")
##### EPIDEMIC LENGTH ####
rbind(I00, I01, I02) %>% 
  ggplot() +
  geom_histogram(aes(day, fill = Scenario)) +
  scale_fill_manual(values = ColPal) +
  facet_grid(~Scenario) +
  ggtitle(" Epidemic duration")
```

### Use of PPE by residents and staff

```{r}
#### 60% residents/ 90% staff
D03 <- ReadSims(paste0(p, "03/EC/"))
S03 <- PlotCycles(D03, var = "I", col = "red3")
I03 <- CycleSums(D03) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Staff priority')
### 90% residents/ 60% staff
D04 <- ReadSims(paste0(p, "04/EC/"))
S04 <- PlotCycles(D04, var = "I", col = "red3")
I04 <- CycleSums(D04) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Residents priority')


S03; S04
##### NUMBER OF INFECTED ####
rbind(I03, I04) %>%
  ggplot() +
  geom_boxplot(aes(y = Cumulative_I_r, fill = Scenario)) +
  scale_fill_manual(values = ColPal) +
  ggtitle("Epidemic Size")
##### EPIDEMIC LENGTH ####
rbind(I03, I04) %>% 
  ggplot() +
  geom_histogram(aes(day, fill = Scenario)) +
  scale_fill_manual(values = ColPal) +
  facet_grid(~Scenario) +
  ggtitle(" Epidemic duration")
```


## Frequency of testing

Scenarios:

```{r}
p <- "../../Data/SimsOut/Testing/"
D00 <- ReadSims(paste0(p, "00/EC/"))
S00 <- PlotCycles(D00, var = "I", col = "red3")
I00 <- CycleSums(D00) %>%
  .$cycle_TTE %>%
  mutate(Scenario = '00')

D01 <- ReadSims(paste0(p, "01/EC/"))
S01 <- PlotCycles(D01, var = "I", col = "red3")
I01 <- CycleSums(D01) %>%
  .$cycle_TTE %>%
  mutate(Scenario = '01')

D02 <- ReadSims(paste0(p, "02/EC/"))
S02 <- PlotCycles(D02, var = "I", col = "red3")
I02 <- CycleSums(D02) %>%
  .$cycle_TTE %>%
  mutate(Scenario = '02')

S00; S01; S02

rbind(I00, I01, I02) %>%
  ggplot() +
  geom_boxplot(aes(y = Cumulative_I_r, fill = Scenario)) +
  scale_fill_manual(values = ColPal) 

rbind(I00, I01, I02) %>%
  ggplot() +
  geom_boxplot(aes(y = Cumulative_H, fill = Scenario)) +
  scale_fill_manual(values = ColPal)  +
  ggtitle("Hospitalizations")

rbind(I00, I01, I02) %>% 
  ggplot() +
  geom_histogram(aes(day, fill = Scenario)) +
  facet_grid(~Scenario) +
  scale_fill_manual(values = ColPal) 

# rbind(I00, I01, I02) %>%
#   mutate(HospRate = Cumulative_H/(Cumulative_I_r+Cumulative_I_s)) %>%
#   ggplot() +
#   geom_boxplot(aes(y = HospRate, fill = Scenario)) +
#   scale_fill_manual(values = ColPal)  +
#   ggtitle("Hospitalizations")
```


```{r}
rbind(I00, I01, I02) %>%
  group_by(Scenario) %>%
  summarise_at(.vars = c('I', 'day'), .funs = c(mean)) %>%
  mutate_at(.vars = c('I', 'day'), .funs = ~(.[1] - .)/.[1])
```

## Probability of introduction

```{r}
p <- "../../Data/SimsOut/Introduction/"
D00 <- ReadSims(paste0(p, "00/EC/"))
S00 <- PlotCycles(D00, var = "I", col = "red3")
I00 <- CycleSums(D00) %>%
  .$cycle_TTE %>%
  mutate(Scenario = '00')

D01 <- ReadSims(paste0(p, "01/EC/"))
S01 <- PlotCycles(D01, var = "I", col = "red3")
I01 <- CycleSums(D01) %>%
  .$cycle_TTE %>%
  mutate(Scenario = '01')

D02 <- ReadSims(paste0(p, "02/EC/"))
S02 <- PlotCycles(D02, var = "I", col = "red3")
I02 <- CycleSums(D02) %>%
  .$cycle_TTE %>%
  mutate(Scenario = '02')

S00; S01; S02

rbind(I00, I01, I02) %>%
  ggplot() +
  geom_boxplot(aes(y = Cumulative_I_r, fill = Scenario)) +
  scale_fill_manual(values = ColPal) 

rbind(I00, I01, I02) %>%
  ggplot() +
  geom_boxplot(aes(y = Cumulative_H, fill = Scenario)) +
  scale_fill_manual(values = ColPal)  +
  ggtitle("Hospitalizations")

rbind(I00, I01, I02) %>% 
  ggplot() +
  geom_histogram(aes(day, fill = Scenario)) +
  facet_grid(~Scenario) +
  scale_fill_manual(values = ColPal) 
```


## Vaccination


```{r}
p <- "../../Data/SimsOut/Vaccination/"
D00 <- ReadSims(paste0(p, "00/EC/"))
S00 <- PlotCycles(D00, var = "I", col = "red3")
I00 <- CycleSums(D00) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'No vaccination')

D01 <- ReadSims(paste0(p, "01/EC/"))
S01 <- PlotCycles(D01, var = "I", col = "red3")
I01 <- CycleSums(D01) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Staff Vaccination')

D02 <- ReadSims(paste0(p, "02/EC/"))
S02 <- PlotCycles(D02, var = "I", col = "red3")
I02 <- CycleSums(D02) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Resident Vaccination')

D03 <- ReadSims(paste0(p, "03/EC/"))
S03 <- PlotCycles(D03, var = "I", col = "red3")
I03 <- CycleSums(D03) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Staff+Resident Vaccination')

S00; S01; S02; S03

rbind(I00, I01, I02, I03) %>%
  ggplot() +
  geom_boxplot(aes(y = Cumulative_I_r, fill = Scenario)) +
  scale_fill_manual(values = ColPal) 

rbind(I00, I01, I02, I03) %>%
  ggplot() +
  geom_boxplot(aes(y = Cumulative_H, fill = Scenario)) +
  scale_fill_manual(values = ColPal)  +
  ggtitle("Hospitalizations")

rbind(I00, I01, I02, I03) %>% 
  ggplot() +
  geom_histogram(aes(day, fill = Scenario)) +
  facet_grid(~Scenario) +
  scale_fill_manual(values = ColPal) 
```




| Scenario | Testing Freq | PPE effect | PPE p Res | PPE p Staff |
| :------- | :----------- | :--------- | :-------- | :---------- |
| 00       | 7 days       | 0.80       | 90%       | 90%         |

Using ODEs to represent the immune response is very resource consuming, maybe we can use a simpler approach like a constant that varies depending on some tresholds (i.e. first dose, second dose, end of immune coverage, etc...)
```{r}
k <- 0.000004
Day <- 1:300

y <- x*k

y <- lapply(Day, function(x){
  # x <- Day[1]
  k <- ifelse(x < 10, 0.00001, 0.01)
  o <- ifelse(x > 120, (1-0.1), (1-0.000001))
  
  y <- (x^3*k*o)/1000
  y <- ifelse(y > 0.8, 0.8, y)
}) %>% unlist()


y[300]
plot(y~Day)
```
