---
title: "Simulation Outputs"
output: html_notebook
---

# Setup

```{r}
### Libraries
library(dplyr); library(ggplot2); library(ggpubr);library(Pabloverse); library(sf)
library(rpart); library(randomForest); library(caret)
#Total population
N <- 170 + 174
# ==============================================================================
# FUNCTIONS
# ==============================================================================
# Read Simulations
# ------------------------------------------------------------------------------
ReadSims <- function(dir){
  # dir = paste0(p, "00/EC/")
  f <- list.files(dir, full.names = TRUE)
  L <- lapply(1:length(f), function(x){
    read.csv(f[x], fileEncoding = 'UTF-8') %>% # read files
      mutate(Sim = x, day = ceiling(cycle/24)) %>% # create variable for sim number and day
      group_by(Sim, day) %>% # group by simulation and day
      summarise_all(.funs = max) %>%# get the max for all the records.
      ungroup()
    })
  
  N_sim <- lapply(L, nrow) %>% unlist() %>% max(.)
  
  L <- lapply(L, function(x){
    d <- N_sim - nrow(x)
      x %>%
        slice(c(1:nrow(.), rep(nrow(.), each = d))) %>%
        mutate(day = 1:n())
  })
  L %>%
    do.call(rbind, .)
}
# Functions for getting quantiles
# ------------------------------------------------------------------------------
Q05 <- function(sims) quantile(sims, 0.05)
Q25 <- function(sims) quantile(sims, 0.25)
Q75 <- function(sims) quantile(sims, 0.75)
Q95 <- function(sims) quantile(sims, 0.95)

# Function for summarizing the cycles
# ------------------------------------------------------------------------------
CycleSums <- function(sims){
  # sims = D00
  cycle_IQR <- sims %>%
    dplyr::select(-Sim) %>%
    group_by(day) %>%
    summarise_all(.funs = c(Median = median, Q25 = Q25, Q75 = Q75))
  
  cycle_TTE <- sims %>%
    group_by(Sim) %>%
    filter(I == max(I)) %>%
    filter(cycle == max(cycle)) %>%
    mutate(day = floor(cycle/24),
           Cumulative_I = Cumulative_I_r + Cumulative_I_s,
           InfectionRate = Cumulative_I/N) %>%
    distinct()
  
  return(list(cycle_IQR = cycle_IQR, cycle_TTE = cycle_TTE))
}

# Function for the plots
# ------------------------------------------------------------------------------
PlotCycles <- function(sims, var, col, y_lim){
  # sims = D00; var = "I"; col = "red3"
  # y_lab = ifelse(grepl("_P", var), "Infected \n pig herds", "Infected \n wild boar")
  p = sims %>%
    CycleSums() %>%
    .$cycle_IQR %>%
    ggplot(aes(x = day)) +
    geom_line(aes(y = eval(parse(text = paste0(var, '_Median')))),
      col = col, lwd = 1) +
    geom_ribbon(aes(
      ymin = eval(parse(text = paste0(var, '_Q25'))),
      ymax = eval(parse(text = paste0(var, '_Q75')))),
      alpha = 0.3, fill = col) +
    ylab("Number of Infected") +
    theme_minimal() 
    # ylab(y_lab) +
  #   xlab("Days") +
  #   theme(legend.position = "none",
  #     axis.title.y = element_text(angle = 0, vjust = 0.5))
  # if( !missing(y_lim) ) p = p + ylim(y_lim)
  p
  
}
#### Function for time to eradication ####
#----------------------------------------#
TE_data <- function(data){
  data %>%
    mutate(day = floor(cycle/24)) %>%
    group_by(Sim, day) %>%
    summarise(I = max(I)) %>%
    group_by(Sim) %>%
    filter(I == max(I)) %>%
    filter(day == min(day))
}

#### Plot the outputs ####
#-------------------------------#
Plots <- function(x, main = ''){
  ##### NUMBER OF INFECTED ####
  CumI_p <- x %>%
  ggplot() +
  geom_boxplot(aes(y = InfectionRate, fill = Scenario), alpha = 0.6) +
  scale_fill_manual(values = ColPal) +
  ylab("Infection rate") +
  ggtitle("Epidemic Size") +
    theme_minimal() +
    theme(axis.text.x = element_blank())
  ##### EPIDEMIC LENGTH ####
  EpiL_p <- x %>% 
    ggplot() +
  geom_histogram(aes(day, fill = Scenario, col = Scenario), alpha = 0.4, binwidth = 5) +
  scale_fill_manual(values = ColPal) +
    scale_color_manual(values = ColPal) +
  facet_grid(~Scenario) +
  ggtitle(" Epidemic duration") +
    theme_minimal()

  if(length(unique(x$Scenario)) == 1){
    ggarrange(CumI_p, EpiL_p, ncol = 2, common.legend = T) %>%
      annotate_figure(text_grob(main, color = "grey20", face = "bold", size = 14)) 
  }else{
    ggarrange(CumI_p, EpiL_p, nrow = 2, common.legend = T) %>%
      annotate_figure(text_grob(main, color = "grey20", face = "bold", size = 14)) 
  }
}

#### Summary table ####
#-------------------------------#
Sum_Tbl <- function(x){
  x %>%
    group_by(Scenario) %>%
    summarise_at(.vars = c('InfectionRate', 'day', 'Cumulative_I', 'Cumulative_I_r', 'Cumulative_I_s', 'Cumulative_H', 'D'), .funs = c(m = median, Q05 = Q05, Q95 = Q95)) %>%
    mutate(across(where(is.numeric), ~round(., 2)),
           InfectionRate = paste0(InfectionRate_m, ' (', InfectionRate_Q05, ',', InfectionRate_Q95, ')'),
           day = paste0(day_m, ' (', day_Q05, ',', day_Q95, ')'),
           Cumulative_I = paste0(Cumulative_I_m, ' (', Cumulative_I_Q05, ',', Cumulative_I_Q95, ')'),
           Cumulative_I_r = paste0(Cumulative_I_r_m, ' (', Cumulative_I_r_Q05, ',', Cumulative_I_r_Q95, ')'),
           Cumulative_I_s = paste0(Cumulative_I_s_m, ' (', Cumulative_I_s_Q05, ',', Cumulative_I_s_Q95, ')'),
           Cumulative_H = paste0(Cumulative_H_m, ' (', Cumulative_H_Q05, ',', Cumulative_H_Q95, ')'),
           Cumulative_D = paste0(D_m, ' (', D_Q05, ',', D_Q95, ')')) %>%
    select(Scenario, day, InfectionRate, Cumulative_I, Cumulative_I_r, Cumulative_I_s, Cumulative_H, Cumulative_D)
}
```


# Test
```{r Test}
p <- "../../Data/SimsOut/Test/"
ColPal <- c("grey40")
### Test
Bb <- ReadSims(p)
Sb <- PlotCycles(Bb, var = "I", col = "red3")
Ib <- CycleSums(Bb) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Baseline')

BTbl <- Sum_Tbl(Ib)
Plots(Ib, 'Baseline Scenario')
Sb
BTbl
```


# Baseline

```{r}
p <- "../../Data/SimsOut/Baseline/"
ColPal <- c("grey40")
### Baseline
Bb <- ReadSims(p)
BIp <- PlotCycles(Bb, var = "I", col = "red3")
BCIp <- Bb %>%
  mutate(CumI = Cumulative_I_r + Cumulative_I_s) %>% 
  PlotCycles(., var = 'CumI', col = 'red3')

Ib <- CycleSums(Bb) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Baseline')

BTbl <- Sum_Tbl(Ib)
Plots(Ib, 'Baseline Scenario') %>%
  ggsave(filename = "../../Documentation/Figures/SensitivityAnalysis/Baseline.png", width = 8, height = 4)
BIp; BCIp
BTbl
```



# Sensitivity analysis
## Transmission probability

00 - 0.50
01 - 0.52
02 - 0.55

```{r Transmission}
p <- "../../Data/SimsOut/SensitivityAnalysis/TransmissionProbability/"
ColPal <- c("#B284E3", "grey40", "#F28C8C")
### 3% Transmission Probability
D00 <- ReadSims(paste0(p, "Low/"))
S00 <- PlotCycles(D00, var = "I", col = "red3")
I00 <- CycleSums(D00) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Low transmission')
### 7% Introduction Probability
D01 <- ReadSims(paste0(p, "High/"))
S01 <- PlotCycles(D01, var = "I", col = "red3")
I01 <- CycleSums(D01) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'High transmission')
# ### 10% Introduction Probability
# D02 <- ReadSims(paste0(p, "02/"))
# S02 <- PlotCycles(D02, var = "I", col = "red3")
# I02 <- CycleSums(D02) %>%
#   .$cycle_TTE %>%
#   mutate(Scenario = 'High transmission')

x <- rbind(I00, Ib, I01) %>%
  mutate(Scenario = factor(Scenario, levels = c('Low transmission', 'Baseline', 'High transmission'))) 

TTbl <- Sum_Tbl(x)
x %>%
  Plots('Transmission Probability') %>%
  ggsave(filename = "../../Documentation/Figures/SensitivityAnalysis/Transmission.png", width = 9, height = 5)
TTbl
```


## Introduction probability

00 - 0.05
01 - 0.1
02 - 0.15

```{r Introduction}
p <- "../../Data/SimsOut/SensitivityAnalysis/IntroductionProbability/"
ColPal <- c("#704500", 'grey40', "#076600")
### 1% Introduction Probability
D00 <- ReadSims(paste0(p, "Low/"))
S00 <- PlotCycles(D00, var = "I", col = "red3")
I00 <- CycleSums(D00) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Low Introduction Probability')
### 10% Introduction Probability
D01 <- ReadSims(paste0(p, "High/"))
S01 <- PlotCycles(D01, var = "I", col = "red3")
I01 <- CycleSums(D01) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'High Introduction Probability')
### 10% Introduction Probability
# D02 <- ReadSims(paste0(p, "02/"))
# S02 <- PlotCycles(D02, var = "I", col = "red3")
# I02 <- CycleSums(D02) %>%
#   .$cycle_TTE %>%
#   mutate(Scenario = '10% Introduction Probability')

x <- rbind(I00, Ib, I01) %>%
  mutate(Scenario = factor(Scenario, levels = c('Low Introduction Probability', 'Baseline', 'High Introduction Probability'))) 

ITbl <- Sum_Tbl(x)

x %>%
  Plots(main = "Probability of Introduction")  %>%
  ggsave(filename = "../../Documentation/Figures/SensitivityAnalysis/Introduction.png", width = 9, height = 5)
ITbl
```

## Detection probability

00 - 75% detection probability
01 - 80% detection probability
02 - 90% Detection probability

```{r DetectionProbability SA}
p <- "../../Data/SimsOut/SensitivityAnalysis/DetectionProbability/"
ColPal <- c("#00827E", 'grey40', "#00CFB7")
### 75% Detection Probability
D00 <- ReadSims(paste0(p, "Low/"))
S00 <- PlotCycles(D00, var = "I", col = "red3")
I00 <- CycleSums(D00) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Low Detection Probability')
## 85% Detection Probability
D01 <- ReadSims(paste0(p, "High/"))
S01 <- PlotCycles(D01, var = "I", col = "red3")
I01 <- CycleSums(D01) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'High Detection Probability')


x <- rbind(I00, Ib, I01) %>%
  mutate(Scenario = factor(Scenario, levels = c('Low Detection Probability', 'Baseline', 'High Detection Probability')))

DTbl <- Sum_Tbl(x)
x %>%
  Plots(main = "Probability of Detection") %>%
  ggsave(filename = "../../Documentation/Figures/SensitivityAnalysis/ProbDetection.png", width = 9, height = 5)
DTbl
```


## PPE Effect

00 - LB
01 - Estimate
02 - UB (0.2408)

```{r FaceMasks}
p <- "../../Data/SimsOut/SensitivityAnalysis/FaceMasks/"
ColPal <- c("#5C9669", "#6A918C", "#7280B3")
### 1% Introduction Probability
D00 <- ReadSims(paste0(p, "High/"))
S00 <- PlotCycles(D00, var = "I", col = "red3")
I00 <- CycleSums(D00) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'High effect PPE')
### 5% Introduction Probability
D01 <- ReadSims(paste0(p, "Low/"))
S01 <- PlotCycles(D01, var = "I", col = "red3")
I01 <- CycleSums(D01) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Low effect PPE')

x <- rbind(I00, Ib, I01) %>%
  mutate(Scenario = factor(Scenario, levels = c('High effect PPE', 'Baseline', 'Low effect PPE'))) 

PPETbl <- Sum_Tbl(x)
x %>% 
  Plots('Effect of PPE') %>%
  ggsave(filename = "../../Documentation/Figures/SensitivityAnalysis/PPE.png", width = 9, height = 5)
PPETbl
```


## Testing Frequency ()

```{r}
p <- "../../Data/SimsOut/SensitivityAnalysis/TestingFreq/"
ColPal <- c("#5C9669", "#6A918C", "#7280B3")
### 1% Introduction Probability
D00 <- ReadSims(paste0(p, "Testing5/"))
S00 <- PlotCycles(D00, var = "I", col = "red3")
I00 <- CycleSums(D00) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Every 5 days')
### 5% Introduction Probability
D01 <- ReadSims(paste0(p, "Testing3/"))
S01 <- PlotCycles(D01, var = "I", col = "red3")
I01 <- CycleSums(D01) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Every 3 days')

x <- rbind(I00, Ib, I01) %>%
  mutate(Scenario = factor(Scenario, levels = c('Baseline', 'Every 5 days', 'Every 3 days'))) 

TFTbl <- Sum_Tbl(x)
TFTbl
x %>% 
  Plots('Testing Frequency') %>%
  ggsave(filename = "../../Documentation/Figures/SensitivityAnalysis/TestingFreq.png", width = 9, height = 5)
```


## Vaccine Effect

```{r}
p <- "../../Data/SimsOut/SensitivityAnalysis/VaccineEffect/"

ColPal <- c("#5C9669", "#6A918C", "#7280B3")
### Same vaccine effect for residents and staff
D00 <- ReadSims(paste0(p, "Equal/"))
S00 <- PlotCycles(D00, var = "I", col = "red3")
I00 <- CycleSums(D00) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Same vaccine effect')
### Different vaccine effect for residents and staff (Pfizer)
D01 <- ReadSims(paste0(p, "Pfizer/"))
S01 <- PlotCycles(D01, var = "I", col = "red3")
I01 <- CycleSums(D01) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Pfizer')
### Different vaccine effect for residents and staff (Pfizer)
D02 <- ReadSims(paste0(p, "Moderna/"))
S02 <- PlotCycles(D02, var = "I", col = "red3")
I02 <- CycleSums(D02) %>%
  .$cycle_TTE %>%
  mutate(Scenario = 'Moderna')

x <- rbind(I00, I01, I02) %>%
  mutate(Scenario = factor(Scenario, levels = c('Same vaccine effect', 'Pfizer', 'Moderna'))) 

VeTbl <- Sum_Tbl(x)

x %>%
  Plots('Vaccine Effect') %>%
  ggsave(filename = "../../Documentation/Figures/SensitivityAnalysis/VaccinationEf.png", width = 9, height = 5)
VeTbl
```


### Summary 

```{r SA Summary}
rbind(BTbl, TTbl, ITbl, DTbl, PPETbl, TFTbl, VeTbl) %>%
  distinct() %>%
write.csv(., "../../Documentation/Tables/SA_sum.csv", row.names = F)
```




# Scenario Modeling

## Function for plots
```{r}
PlotScenarios <- function(x, v, main){
  CumI_p <- x %>%
  ggplot() +
  geom_boxplot(aes(y = InfectionRate, fill = eval(parse(text=v))), alpha = 0.6) +
  scale_fill_manual(values = ColPal) +
  facet_wrap(~cl) +
  theme_minimal()+
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        strip.background = element_rect(colour="black",
                                        fill="grey90")) +
    ylab("Proportion of Infected") +
    labs(fill = v)

  EpiL_p <- x %>%
    ggplot() +
    geom_histogram(aes(day, fill = eval(parse(text=v)), color = eval(parse(text=v))),
                   alpha = 0.6,
                   binwidth = 5) +
    scale_fill_manual(values = ColPal) +
    scale_color_manual(values = ColPal) +
    facet_wrap( ~ cl + eval(parse(text=v)), nrow = 1) +
    ggtitle(" Epidemic duration") +
    theme_minimal() +
    theme(strip.background = element_blank(), strip.text = element_blank()) +
    labs(fill = v)
  
  ggarrange(CumI_p, EpiL_p, nrow = 2, common.legend = T) %>%
    annotate_figure(text_grob(
      main,
      color = "grey20",
      face = "bold",
      size = 14
    ))
}

```


## Testing Frequency

```{r}
ColPal <- c("#C70704", "#BAB700", "#008C0C")
p <- "../../Data/SimsOut/Scenarios/TF/"
d <- list.files(p)
DL <- lapply(paste0(p,d), function(x){
  D <- ReadSims(x) %>%
    CycleSums(.) %>%
    .$cycle_TTE %>%
    mutate(Scenario = factor(gsub(p, '', x), levels = c('HI_7', 'HI_5', 'HI_3', 'MI_7', 'MI_5', 'MI_3', 'LI_7', 'LI_5', 'LI_3')))
}) %>%
  do.call(rbind,.) %>% 
  mutate(cl = factor(gsub('_.*', '', Scenario), levels = c('HI', 'MI', 'LI')),
         cl = recode(cl, HI = 'High', MI = 'Medium', LI = 'Low'),
    TestingInterval = factor(gsub('.*_', '', Scenario), levels = c('7', '5', '3')),
    TestingInterval = recode(TestingInterval, `7` = '7 Days', `5` = '5 Days', `3` = '3 Days'))


PlotScenarios(x = DL, v = 'TestingInterval', main = "Testing Interval") %>%
  ggsave(filename = "../../Documentation/Figures/Scenarios/TF.png", width = 9, height = 6)
Sum_Tbl(DL)  %>%
  write.csv(., "../../Documentation/Tables/TF.csv", row.names = F)
```


## Vaccine Effect

```{r}
ColPal <- c("#5C9669", "#6A918C", "#7280B3")
p <- "../../Data/SimsOut/Scenarios/VE/"
d <- list.files(p)
DL <- lapply(paste0(p,d), function(x){
  D <- ReadSims(x) %>%
    CycleSums(.) %>%
    .$cycle_TTE %>%
    mutate(Scenario = factor(gsub(p, '', x), levels = c('HI_E', 'HI_P', 'HI_M', 'MI_E', 'MI_P', 'MI_M', 'LI_E', 'LI_P', 'LI_M')))
}) %>%
  do.call(rbind,.) %>% 
  mutate(cl = factor(gsub('_.*', '', Scenario), levels = c('HI', 'MI', 'LI')),
         cl = recode(cl, HI = 'High', MI = 'Medium', LI = 'Low'),
    VaccineEffect = factor(gsub('.*_', '', Scenario), levels = c('E', 'P', 'M')))


PlotScenarios(x = DL, v = 'VaccineEffect', main = "Vaccine Effect") %>%
  ggsave(filename = "../../Documentation/Figures/Scenarios/VE.png", width = 9, height = 6)
Sum_Tbl(DL) %>%
  write.csv(., "../../Documentation/Tables/VE.csv", row.names = F)
```

## Vaccine Distribution

```{r}
ColPal <- c("#414042", "#8C8700", "#5D0DB3")
p <- "../../Data/SimsOut/Scenarios/VD/"
d <- list.files(p)
DL <- lapply(paste0(p,d), function(x){
  D <- ReadSims(x) %>%
    CycleSums(.) %>%
    .$cycle_TTE %>%
    mutate(Scenario = factor(gsub(p, '', x), levels = c('HI_E', 'HI_R', 'HI_S', 'MI_E', 'MI_R', 'MI_S', 'LI_E', 'LI_R', 'LI_S')))
}) %>%
  do.call(rbind,.) %>% 
  mutate(cl = factor(gsub('_.*', '', Scenario), levels = c('HI', 'MI', 'LI')),
         cl = recode(cl, HI = 'High', MI = 'Medium', LI = 'Low'),
    VaccineDistribution = factor(gsub('.*_', '', Scenario), levels = c('E', 'R', 'S')),
    VaccineDistribution = recode(VaccineDistribution, E = 'Equal Distribution', R = 'Resident Priority', S = 'Staff Priority'))

PlotScenarios(x = DL, v = 'VaccineDistribution', main = "Vaccine Distribution") %>%
  ggsave(filename = "../../Documentation/Figures/Scenarios/VD.png", width = 9, height = 6)
Sum_Tbl(DL) %>%
  write.csv(., "../../Documentation/Tables/VD.csv", row.names = F)
```

```{r}
Sum_Tbl(DL)
```

# Version 2

```{r Functions}
###### For READING FILES ########
# Function to read the sims
# ---------------------------------------
ReadSims <- function(d) {
  f <- list.files(d, full.names = T)
  D <- lapply(f, function(x) {
    read.csv(x)
  }) %>%
    do.call(rbind, .)
  return(D)
}
# Function to read the directories
# ------------------------------------
ReadDirs <- function(d){
  dirs <- list.dirs(d, recursive = F)
  Ld <- lapply(dirs, ReadSims)
  names(Ld) <- gsub(d, '', dirs) %>%  gsub('([^A-z])', '', .)
  return(Ld)
}
# Function to get the plots 
# ----------------------------------
RFCART <- function(data, f, main = '', seed = 1, palette  ='-RdYlGn'){
  PL <- list()
  
  set.seed(seed)
  # Split the data train/test
  ind <- sample(2, nrow(data), replace = TRUE, prob = c(0.7, 0.3))
  train <- data[ind==1,]
  test <- data[ind==2,]
  # Random Forest model fit
  rf <- randomForest::randomForest(f, data=train, proximity=TRUE) 
  print(rf)
  
  # Variable importance
  PL[[2]] <- importance(rf) %>%
    data.frame() %>% 
    mutate(variable = rownames(.), RelImpt = IncNodePurity/sum(IncNodePurity)) %>%
    ggplot(aes(x = reorder(variable, RelImpt), y = RelImpt)) +
    geom_col() +
    coord_flip() +
    labs(x = '', y = 'Relative Importance', title = main) +
    theme_minimal() +
    theme(axis.text=element_text(size=14),
        axis.title=element_text(size=16,face="bold"))
  
  # tr <- tree::tree(f, data=data)
  # plot(tr); text(tr)
  fit <- rpart(f, data=data, method = 'anova')
  PL[[1]] <- rpart.plot::rpart.plot(fit, type = 4, box.palette = palette, branch.lty = 2)
  
  return(PL)
}
ICurveP <- function(x){
  d$EC %>% 
    mutate(day = floor(cycle/24)) %>%
    # group_by(seed) %>% 
    # mutate(L = n()) %>% ungroup() %>% mutate(mL = max(L), dL = mL - L) %>%  group_by(seed) %>% slice(c(1:n(),rep(n(), max(dL)))) %>% 
    # ungroup() %>% arrange(seed, day) %>% 
    group_by(day, {{x}}) %>% 
    summarise(MeanCI = mean(Cumulative_I), MedianCI = median(I)) %>% 
   ggplot() +
  geom_line(aes(day, MeanCI, col = factor({{x}})), lwd = 0.5) +
  Pabloverse::Theme1()
}


```


```{r load the data}
p <- "../GAMA_NHCOVID/NH_COVID/models/results/"
d <- ReadDirs(p)
Outcomes <- c('I', 'Cumulative_I', 'I_r', 'I_s')
Var <- c('GlobalShedding_p', 'Introduction_p', 'TestingFreq', 'PPE_OR', 'Test_sensitivity', 'vaccination_dist', 'VaccineEff')
```

```{r}
x <- unique(d$EC$PPE_OR)

d$EC %>% 
  filter(PPE_OR == x[2]) %>% #c('0.304', '0.380', '0.456')
  group_by(cycle) %>% 
  summarise_at(c('Cumulative_I'), .funs = ~mean(., na.rm = T)) %>% 
  ggplot(aes(x = cycle)) +
  geom_line(aes(y = Cumulative_I))
```


```{r}
d$EC %>% 
    mutate(day = floor(cycle/24)) %>% 
    group_by(seed) %>% 
    mutate(L = n()) %>% ungroup() %>% mutate(mL = max(L), dL = mL - L) %>%  group_by(seed) %>% slice(c(1:n(),rep(n(), max(dL)))) %>% 
    ungroup() %>% arrange(seed, day) %>% 
    group_by(day, GlobalShedding_p) %>% 
    summarise(MeanCI = mean(Cumulative_I), MedianCI = median(I)) %>% 
  arrange(GlobalShedding_p, day)
   ggplot() +
  geom_line(aes(day, MeanCI, col = factor(GlobalShedding_p)), lwd = 0.5) +
  Pabloverse::Theme1()
```


```{r univar}
ICurveP(GlobalShedding_p)
ICurveP(TestingFreq)
ICurveP(PPE_OR)
ICurveP(VaccineEff)
```

```{r bivariate}
d$EC %>% 
  # filter(p2 == 1) %>% 
    group_by(cycle, GlobalShedding_p, VaccineEff) %>% 
    summarise(MeanCI = mean(Cumulative_I), MedianCI = median(Cumulative_I)) %>% 
   ggplot() +
  geom_line(aes(cycle, MeanCI, col = factor(VaccineEff)), lwd = 0.6) +
  facet_wrap(~GlobalShedding_p, scales = 'free_y') +
  Pabloverse::Theme1() +
  theme(legend.position = 'top')
```


```{r}
ds <- d$EC %>% 
  # mutate_at(c('Cumulative_I', 'Cumulative_I_r','Cumulative_I_s', 'Cumulative_H', 'D'), .funs = ~./N) %>% 
  ## THIS CHUNK IS TO REMOVE THE TAILS OF 95%
  # group_by(seed) %>% 
  # mutate(Cumulative_I_c = max(Cumulative_I)) %>% data.frame() %>%
  # filter(Cumulative_I_c < quantile(Cumulative_I_c, probs = 0.95), Cumulative_I_c > quantile(Cumulative_I_c, probs = 0.05)) %>% data.frame() %>% 
  group_by(seed, .dots=lapply(Var, as.symbol)) %>% 
  summarise_at(c('Cumulative_I', 'Cumulative_I_r','Cumulative_I_s', 'Cumulative_H', 'D', 'LastInfection'), .funs = max) %>% 
  ungroup() %>% 
  mutate_at(.vars = Var, .funs = factor) %>%
  mutate(LastInfection = (LastInfection/24)+7) %>% 
  select(-seed)


f1 <- Cumulative_I ~ GlobalShedding_p + Introduction_p + TestingFreq + PPE_OR + Test_sensitivity + vaccination_dist + VaccineEff
f2 <- Cumulative_I_r ~ GlobalShedding_p + Introduction_p + TestingFreq + PPE_OR + Test_sensitivity + vaccination_dist + VaccineEff
f3 <- Cumulative_I_s ~ GlobalShedding_p + Introduction_p + TestingFreq + PPE_OR + Test_sensitivity + vaccination_dist + VaccineEff
f4 <- LastInfection ~ GlobalShedding_p + Introduction_p + TestingFreq + PPE_OR + Test_sensitivity + vaccination_dist + VaccineEff

RFCART(f = f1 ,data = ds, main = 'Variable contribution for cumulative infected')
RFCART(f = f2 ,data = ds, main = 'Variable contribution for cumulative infected (residents)')
RFCART(f = f3 ,data = ds, main = 'Variable contribution for cumulative infected (staff)')
RFCART(f = f4 ,data = ds, main = 'Variable contribution for las day of infection')
```


## Scenarios

```{r}
ScenarioSum <- function(scenario, var){
  # scenario <- 'VacinationReplacement'; var = 'pInfected'
  ds %>% 
    mutate(Testing5 = ifelse(TestingFreq %in% c('3','5'), 1, 0),
           Testing3 = ifelse(TestingFreq == '3', 1, 0)) %>% 
    # mutate_at(.vars = scenarios, ~recode(., `Yes` = '1', `No` = '0')) %>% 
    # mutate(VacTest = ifelse(VacinationReplacement == 1 & ReplacementTesting == 1, 1, 0),
    #        ReplacementTesting = ifelse(ReplacementTesting == 1, 0, 1)) %>% 
    group_by(eval(parse(text = scenario))) %>%
  summarise(Var = mean(eval(parse(text = var)))) %>%
    rename(scenario = `eval(parse(text = scenario))`) %>% 
  tidyr::spread(data = ., key = scenario, Var) %>% 
  mutate(S = scenario)
}

ScenarioSum(scenario = 'Testing3', var = 'Cumulative_I')
```


```{r}
scenarios <- c('EmergencyVaccination', 'movement_restrictions', 'detection14', 'detection7', 'Culling')

ScenarioSum <- function(scenario, var){
  # scenario <- 'VacinationReplacement'; var = 'pInfected'
  d %>% 
    mutate(detection14 = ifelse(detection_effect == '14', 1, 0),
           detection7 = ifelse(detection_effect == '7', 1, 0),
           Culling = ifelse(CullingRate == '0', 1, 0)) %>% 
    # mutate_at(.vars = scenarios, ~recode(., `Yes` = '1', `No` = '0')) %>% 
    # mutate(VacTest = ifelse(VacinationReplacement == 1 & ReplacementTesting == 1, 1, 0),
    #        ReplacementTesting = ifelse(ReplacementTesting == 1, 0, 1)) %>% 
    group_by(eval(parse(text = scenario))) %>%
  summarise(Var = mean(eval(parse(text = var)))) %>%
    rename(scenario = `eval(parse(text = scenario))`) %>% 
  tidyr::spread(data = ., key = scenario, Var) %>% 
  mutate(S = scenario)
}

Ss <- lapply(scenarios, ScenarioSum, var = 'CumulativeInfected') %>% 
  do.call(rbind, .) %>% 
  rename(Yes = '1', No = '0')


 Pr <- Ss %>%
  mutate(Reduction = abs(round((1 - (Yes/No))*100, 2))) %>% 
  # arrange(desc(`0`))
  # filter(S == 'ConfirmatoryTesting') %>% 
  ggplot(aes(x = S)) +
  geom_bar(aes(y = No), alpha = 0.8, fill = 'red3', col = 'black', stat="identity", width = 0.5) +
  geom_bar(aes(y = Yes), alpha = 0.6, fill = 'green', stat="identity", width = 0.48) +
    geom_text(aes(y = No, label = paste0('-', Reduction, '%')), hjust = 3, col = 'grey90') +
  coord_flip() +
  Theme1() +
  labs(y = '', x = '', title = 'Reduction of interventions in cumulative infected herds')
 
Pr %>%
  ggsave(filename = '../../Docs/Figures/Reduction.png', width = 8, height = 4)
```



```{r}
scenarios <- c('ReplacementTesting', 'PigletVaccination', 'VacinationReplacement', 'HerdClosure')

Ss <- lapply(scenarios, ScenarioSum, var = 'pInfected') %>% 
  do.call(rbind, .) %>% 
  mutate(var = 'Sow Cumulative incidence')

Ss <- Ss %>% 
  rbind(
    lapply(scenarios, ScenarioSum, var = 'FarrowingMortality') %>% 
  do.call(rbind, .) %>% 
    mutate(var = 'Piglets Cumulative incidence')
  )

Ss <- Ss %>%
  rbind(
    lapply(scenarios, ScenarioSum, var = 'LastInfected') %>%
  do.call(rbind, .) %>%
    mutate(var = 'Time to elimination')
  )

Pr <- Ss %>%
  mutate(Reduction = abs(round((1 - (Yes/No))*100, 2))) %>% 
  # arrange(desc(`0`))
  # filter(S == 'ConfirmatoryTesting') %>% 
  ggplot(aes(x = S)) +
  geom_bar(aes(y = No), alpha = 0.8, fill = 'red3', col = 'black', stat="identity", width = 0.5) +
  geom_bar(aes(y = Yes), alpha = 0.6, fill = 'green', stat="identity", width = 0.48) +
    geom_text(aes(y = No, label = paste0('-', Reduction, '%')), hjust = 3, col = 'grey90') +
  coord_flip() +
  facet_wrap(~var, scales = 'free_x') +
  Theme1() +
  labs(y = '', x = '', title = 'Reduction of interventions in outcomes analyzed')


Pr 

```
